Energy and the CES production function

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
fix delta in hand-crafted model

      cesModCSP$coefficients <- 
        c(cesModCSP$coefficients, 
          c(delta_1 = cesModCSP$coefficients["alpha_1"],
            delta = 0,
            rho_1 = 0,
            rho = NA)
        )
      cesModCSP$handcrafted <- TRUE
      class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
      # # Again, we need a customized "naturalCoeffs" attribute so that 
      # # the "naturalCoef" function will do the right thing.
      # # "naturalCoeffs" can be based on the same "naturalCoeffs"
      # # from the Cobb-Douglas model, but a few additions are needed.
      # attr(cesModCSP, "naturalCoeffs") <- 
      #   naturalCoef(cdModCSP) %>%
      #   mutate(
      #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
      #     delta = 1,
      #     rho_1 = 0, 
      #     rho = NA,
      #     sigma_1 = 1,
      #     sigma_12 = 1,
      #     sigma = NA,
      #     sigma_12_3 = NA
      #   )
      # # Add output elasticities (as a function of time) to this model.
      # # This would have been done by a "fortify" function, 
      # # but this is not a typical CES model, so we can't "fortify" it.
      # # Add other metadata, too.
      # cesModCSP$data <- cesModCSP$data %>%
      #   mutate(
      #     oe1 = alphaCSP,
      #     oe2 = betaCSP,
      #     oe3 = 0,
      #     Country = country, 
      #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
      #     energy  = "Without energy",
      #     model   = "CES", 
      #     nest    = "kl",
      #     CSP     = "w/ CSP"
      #   )
      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
    }
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCSP, file=fileNameCSP)
}

>>>>

      cesModCSP$coefficients <- 
        c(cesModCSP$coefficients, 
          c(delta_1 = as.vector(cesModCSP$coefficients["alpha_1"]),
            delta = 1,
            rho_1 = 0,
            rho = NA)
        )
      cesModCSP$handcrafted <- TRUE
      class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
      # # Again, we need a customized "naturalCoeffs" attribute so that 
      # # the "naturalCoef" function will do the right thing.
      # # "naturalCoeffs" can be based on the same "naturalCoeffs"
      # # from the Cobb-Douglas model, but a few additions are needed.
      # attr(cesModCSP, "naturalCoeffs") <- 
      #   naturalCoef(cdModCSP) %>%
      #   mutate(
      #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
      #     delta = 1,
      #     rho_1 = 0, 
      #     rho = NA,
      #     sigma_1 = 1,
      #     sigma_12 = 1,
      #     sigma = NA,
      #     sigma_12_3 = NA
      #   )
      # # Add output elasticities (as a function of time) to this model.
      # # This would have been done by a "fortify" function, 
      # # but this is not a typical CES model, so we can't "fortify" it.
      # # Add other metadata, too.
      # cesModCSP$data <- cesModCSP$data %>%
      #   mutate(
      #     oe1 = alphaCSP,
      #     oe2 = betaCSP,
      #     oe3 = 0,
      #     Country = country, 
      #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
      #     energy  = "Without energy",
      #     model   = "CES", 
      #     nest    = "kl",
      #     CSP     = "w/ CSP"
      #   )
      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
    }
  }
  # Save cost-share theorem models to disk.
  saveRDS(modelsCSP, file=fileNameCSP)
}
